My title

### 2024-11-26 paper/paper.qmd
fixed clean_data.R to save parquet file instead of csv

ggplot(data, aes(x = publish_year, y = rating)) +
  geom_point()
```

>>>>

data2 <- data %>% filter(rating > 4 )

ggplot(data2, aes(x = publish_year, y = rating)) +
  geom_point() +
  theme_minimal()

ggplot(data2, aes(x = rating_count, y = rating)) +
  geom_point()

ggplot(data2, aes(x = pages, y = rating)) +
  geom_point()

ggplot(data2, aes(y = cover)) + 
  geom_bar() +
  theme_minimal()
